Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-28 paper/paper.tex
further works

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
of a linkage function and of SciPy \citep{scipy} for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available and
making it ready for production environments.
It is also designed be runnable
in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
instead of having to run the disambiguation process on the whole signature set.

@@

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance saturates at $0.9845$, which shows not to be better than the best
reported results ($0.9850$). Since the only difference between these two
solutions is the use of Random Forests instead of GBRT as classifiers, this
result suggests there appears to be no significant gain in using one rather
the other. Both tree-based methods show equally good performance.

@@

In this work, we have revisited and validated the general author disambiguation
pipeline introduced in previous independent research work.
The generic approach is composed of three components, whose design and tuning are all critical
to good performance: (i) a blocking function for pre-clustering signatures
and reducing computational complexity, (ii) a linkage function for identifying
signatures with coreferring authors and (iii) the agglomerative clustering of
signatures. Making use of a distinctively large dataset of more than 1 million
crowdsourced annotations, we experimentally study all three components and
propose further improvements. With regards to blocking, we suggest to use
phonetization of author names to increase recall while maintaining low
computational complexity. For the linkage function, we introduce
ethnicity-sensitive features for the automatic tailoring of disambiguation to non-Western
author names whenever necessary. Finally, we explore semi-supervised cut-off
threshold strategies for agglomerative clustering. For all three components,
experiments show that our refinements all yield significantly better author
disambiguation accuracy, thereby encouraging further research in these directions.

Further improvements include ... \glnote{TODO}

>>>>

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
of a linkage function and of SciPy \citep{scipy} for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
It is also designed be runnable
in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
instead of having to run the disambiguation process on the whole signature set.

@@

\textit{Combined best settings.} When all best settings are combined (\ie,
Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
performance saturates at $0.9845$, which shows not to be better than the best
reported results ($0.9850$). Since the only difference between these two
solutions is the use of Random Forests instead of GBRT as classifiers, this
final result suggests that there appears to be no significant gain in using one rather
the other. Both tree-based methods show equally good performance.

@@

In this work, we have revisited and validated the general author disambiguation
pipeline introduced in previous independent research work.
The generic approach is composed of three components, whose design and tuning are all critical
to good performance: (i) a blocking function for pre-clustering signatures
and reducing computational complexity, (ii) a linkage function for identifying
signatures with coreferring authors and (iii) the agglomerative clustering of
signatures. Making use of a distinctively large dataset of more than 1 million
crowdsourced annotations, we experimentally study all three components and
propose further improvements. With regards to blocking, we suggest to use
phonetization of author names to increase recall while maintaining low
computational complexity. For the linkage function, we introduce
ethnicity-sensitive features for the automatic tailoring of disambiguation to non-Western
author names whenever necessary. Finally, we explore semi-supervised cut-off
threshold strategies for agglomerative clustering. For all three components,
experiments show that our refinements all yield significantly better author
disambiguation accuracy.

Overall, these results all encourage further improvements and research. For
blocking, one of the open challenges is to manage signatures with inconsistent
surnames or inconsistent first given names (cases 4 and 5, as described in
Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
For the linkage function, the good results of the proposed features pave the
way for further research  in ethnicity-sensitive author disambiguation. The
automatic fitting of the pipeline to cultures and ethnic groups for which
standard author disambiguation is known to be less efficient (\eg, Chinese
authors with many homonyms)  indeed constitutes a direction of research with
great potential benefits for the concerned scientific communities.
